Solving smooth system of algebraic equations

### 2021-01-17 article/main.tex
work on article

\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{amssymb,amsmath,amsthm} %must be before unicode-math
\usepackage[mathletters]{ucs}
\DeclareUnicodeCharacter{8348}{_t}
\DeclareUnicodeCharacter{8342}{_k}
\DeclareUnicodeCharacter{8339}{_x}
\DeclareUnicodeCharacter{8345}{_n}
\DeclareUnicodeCharacter{7522}{_i}
\DeclareUnicodeCharacter{11388}{_j}
\DeclareUnicodeCharacter{7523}{_r}
\DeclareUnicodeCharacter{7580}{^c}
\DeclareUnicodeCharacter{7496}{^d}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage[autosize]{dot2texi}
\usepackage{multicol}
\setlength{\multicolsep}{0pt}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,tikzmark,decorations.pathreplacing,calc}
\usepackage{adjustbox}

@@

We use on $\PNR$ and $\SNR$ the measure induced by
the chord metric of the unit sphere:
$$d(\overline{x},\overline{y}) = \min\left(
\left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
  \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$

@@

 \end{document}

>>>>

\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{amssymb,amsmath,amsthm} %must be before unicode-math
\usepackage[mathletters]{ucs}
\DeclareUnicodeCharacter{8348}{_t}
\DeclareUnicodeCharacter{8342}{_k}
\DeclareUnicodeCharacter{8339}{_x}
\DeclareUnicodeCharacter{8345}{_n}
\DeclareUnicodeCharacter{7522}{_i}
\DeclareUnicodeCharacter{11388}{_j}
\DeclareUnicodeCharacter{7523}{_r}
\DeclareUnicodeCharacter{7580}{^c}
\DeclareUnicodeCharacter{7496}{^d}
\DeclareUnicodeCharacter{7511}{^t}

\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage[autosize]{dot2texi}
\usepackage{multicol}
\setlength{\multicolsep}{0pt}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,tikzmark,decorations.pathreplacing,calc}
\usepackage{adjustbox}

@@

We use on $\PNR$ and $\SNR$ the measure induced by
the chord metric of the unit sphere:
$$d(\overline{x},\overline{y}) = \min\left(
\left\|{\frac{x}{\|x\|}} - {\frac{y}{\|y\|}}\right\|, \left\|{\frac{x}{\|x\|}} + {\frac{y}{\|y\|}}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$

@@

\appendix

\section{Testing zero in convex hull}

The central test in our algorith is to know if the null vector is in the convex
hull of a given set of vector of $ℝ^d$, or as it is clearly equivalent, in its convex
cone.

More precisely, the problem we want to solve can be defined as follows:
\begin{defi}
  \begin{tabular}{ll}
  Input:& a real $n × d$ matrix $A$. \cr
  Output:& a non nul vector $X ∈ ℝ_+^n$ such that $^tX A = 0$ \cr
  or& a vector $N ∈ ℝ^d$ such that $A N > 0$
  \end{tabular}
\end{defi}

This does correspond to our problem: if zero is in the convex hull of the lines
of the matrix $A$, then we can produce the wanted vector $X∈ ℝ_+^n$. It zero is not in
the convex hull, then we can return the normal $N∈ ℝ^d$ of a linear plane such that
all the lines of $A$ lie on the same side of this plane.

We start the algorithm with an initial vector $X_0∈ ℝ_+^n$, with positive coefficients
summing to one, for instance $X₀=\frac{1}{n}ᵗ(1,1,\dots,1,1)$.
We define $N_i = tX_i A$. We also define a vector $P_0 = 0 ∈ ℝ_+^n $.

The algorithm then perform two kind of steps:

\paragraph*{Conjugate steps}, which are somehow inspired by the conjugate
gradient method.

First we define $J ∈ ℝ_+^n = (1,1,\dots,1,1)$ and $ν(X) = \frac{1}{J.X} X$ which
normalise the vector $X$ to have all its coefficient sum to one. We will use
$ν(X)$ only one non null vector in $ℝ_+^n$.

If for all lines $Aⱼ$ of $A$ we have $Aⱼ.Nᵢ > 0$ then the algorithm
stops and output $N = Nᵢ$. Otherwise we select $Dᵢ = δⱼ$ such that $Aⱼ.Nᵢ ≤ 0$ and minimum.
Then we compute $α>0,β ∈ ℝ$, $X_{i+1) = ν(Xᵢ + αDᵢ+βPᵢ)$, such that
  $\|ᵗX_{i+1} A\|²$ is minimum. We have
  \begin{eqnarray*}
    f(α,β) &=& \|ᵗX_{i+1} A\|² \cr
    &=& \frac{\|ᵗXᵢ A + αᵗDᵢA + βᵗPᵢA\|²}{(1 + α + β)²}\cr
    &=& \frac{\|Nᵢ + αᵗAⱼ + βᵗPᵢA\|²}{(1 + α + βPᵢ.J)²}\cr
    &=& \frac{\|Nᵢ\|² + α² + β²\|ᵗPᵢA\|² + 2 α Nᵢ.Aⱼ + 2 β Nᵢ.ᵗPᵢA + 2αβ Aⱼ.ᵗPᵢA}
    {1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ}\cr
    \frac{∂f(α,β)}{∂α}
    &=& \frac{\begin{array}{cl}
        &(2α + 2 Nᵢ.Aⱼ + 2βAⱼ.ᵗPᵢA)(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)\cr
        - &(\|Nᵢ\|² + α² + β²\|ᵗPᵢA\|² + 2 α Nᵢ.Aⱼ + 2 β Nᵢ.ᵗPᵢA + 2αβ
      Aⱼ.ᵗPᵢA)(2α + 2 + 2βPᵢJ)
      \end{array}}
    {(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)²}\cr
    &=& \frac{
    {(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)²}\cr

  \end{eqnarray*}
\end{document}
